\lightkurve: a Python open source package for NASA's Kepler, K2, and TESS data analysis

### 2018-03-27 paper/ms.tex
add some references on psf modelling

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}
\usepackage{amsmath, amssymb, mathtools, bm}

@@

\title{\lightkurve: a Python package for Kepler \& TESS time series data analysis}

@@

\author{José Vinícius de Miranda Cardoso}
\affiliation{Bay Area Environmental Research Institute \\
Petaluma \\
California, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

@@

In an image with $n$ pixels, where the flux and the center positions of the
$i$-th pixel are denoted as $f_i$ and $(x_i, y_i)$, respectively, the centroids
may be expressed as
\begin{align}
    x^{\star} = \dfrac{\sum_{i=1}^{n} f_i x_i}{\sum_{i=1}^{n}f_i} \\
    y^{\star} = \dfrac{\sum_{i=1}^{n} f_i y_i}{\sum_{i=1}^{n}f_i}.
\end{align}

@@

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{cite}

@@

\title{\lightkurve: a Python open source package for NASA's Kepler, K2, and TESS data analysis}

@@

\author{Jos\'e Vin\'icius de Miranda Cardoso}
\affiliation{Bay Area Environmental Research Institute \\
Petaluma \\
California, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

@@

In an image with $n$ pixels, where the flux and the center positions of the
$i$-th pixel are denoted as $f_i$ and $(x_i, y_i)$, respectively, the centroids
may be expressed as
\begin{align}
    x^{\star} = \dfrac{\sum_{i=1}^{n} f_i x_i}{\sum_{i=1}^{n}f_i},
    ~~y^{\star} = \dfrac{\sum_{i=1}^{n} f_i y_i}{\sum_{i=1}^{n}f_i}.
\end{align}

@@

Point Spread Function (PSF) photometry is the de facto technique to
process crowded-field images~\cite{stetson1987, heasley1999}. In context of Kepler
and K2 missions, Libralato \textit{et al}~\cite{libralato2016} have shown...

The underlying principle of PSF photometry consists in modelling a given crowded
image as a linear combination of individual PSFs and possibly a background model.
On the PSF model itself, it is commonly assumed that the flux
at an arbitrary pixel position increases linearly with the integrated
flux~\cite{stetson1987, heasley1999}.
